---
title: "Weight of Fish"
author: "Leilani Guerrero"
date: "Summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == 'Perch')
Pike = filter(Fish, species == "Pike")
Roach = filter(Fish, species == "Roach")
```

# Predicting Fish Weight

```{r}

pwt = lm(Weight~ Length1+ Length2+ Length3+ Height, data = Perch)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ Length1 + Length2 + Length3 + Height, data = Perch,
             nbest = 4,    # 1 best model for each number of predictors
             nvmax = NULL, # Null for no limit on number of variables
             force.in = NULL, force.out = NULL,
             method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

From this graph I see that the best two predictors of wt for Perch are Length3 and Height


## Perch

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~ Length1 + Length2 + Length3 + Height, data = Perch,
             nbest = 4,    # 1 best model for each number of predictors
             nvmax = NULL, # Null for no limit on number of variables
             force.in = NULL, force.out = NULL,
             method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```



### Best Models


The best model for this case uses all four vaiables 


### Best Two regressor model

From the graph the best two-parameter regressor model is based on Length3 and Height
## Pike

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements